MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-13 docs/paper/out/paper.tex
add @rtobes lines about bio4j and taxonomy
see https://github.com/ohnosequences/metagenomica/issues/26#issuecomment-139849162

>>>>

The hierarchic structure of the taxonomy of the living organisms is a
tree, and, hence, is also a graph in which each node, with the exception
of the root node, has a unique parent node. It led us to model the
taxonomy tree as a graph using the graph database paradigm. Previously
we developed Bio4j \textbf{{[}Pareja-Tobes-2015{]}}, a platform for the
integration of semantically rich biological data using typed graph
models. It integrates most publicly available data linked with sequences
into a set of interdependent graphs to be used for bioinformatics
analysis and especially for biological data.
